Title

### 2024-06-21 paper/main.tex
Updates

\section{A Measure of Association for Mixed Data}
\label{sec:mixed_association}
In the previous section, we outlined measure of associations for different data
types, however we do not have any measure of association for a mixture of
categorical, ordinal, and continuous data. In this section, we develop a
measure of association for mixed data as a generalization of partial
correlation by combining a mixed data residualization approach with canonical
correlations. Similar to partial correlation, we first compute the residuals of
both variables using some machine learning model, and then use a canoncial
correlation based measure of association between the residuals instead of
correlation coefficient.

@@

\subsection{No conditional variables}
When we have no conditonal variables, we need to convert the variables into

\subsection{Conditional Case}
For the conditional case we use an approach similar to partial correlation. We
combine the mixed data residualization approach proposed in Ankan 2023. We then
use a canonical correlation based measure on these residuals to get an effect
size.

@@

\section{Using measure of association for modifying DAGs}
\label{sec:modification}
The idea behind using the measure of association for modifying DAGs is that,
for any given model and a dataset, we can use the condtiional measure of
association to compute the amount of correlation in the data that is still not
explained by the model. Based on this, we can compute how much improvement in
the explanation would happen if we were to add an edge between variables. This
can then be ranked using the maximum improvement. Give some examples here.

@@

\section{Web Tool}
\label{sec:web}
Based on the approach outlined in the previous section, we built a web-based
tool that researchers can upload their dataset to and apply this method to
interactively draw models.

@@

\section{Conclusions}
\subsection{Using LLMs as experts}

>>>>

\section{A Measure of Association for Mixed Data}
\label{sec:mixed_association}

In this section, we develop a (conditional) measure of association for mixed
data as a generalization of partial correlation by combining a mixed data
residualization approach with canonical correlations. Assuming that we need to
compute the association, $ \rho(X, Y; Z) $ between variables $ X $ and $ Y $
conditioned on $ \bm{Z} $. Similar to partial correlations, we first start by
computing the residuals for both $ X $ and $ Y $ using $ \bm{Z} $ as the
predictor variables. When $ \bm{Z} = \emptyset $ we can use a constant value
for $ \bm{Z} $. We use the mixed data residualization approach presented in
Ankan and Textor 2023.

@@

For the conditional case we use an approach similar to partial correlation. We
combine the mixed data residualization approach proposed in Ankan 2023. We then
use a canonical correlation based measure on these residuals to get an effect
size.

@@

\section{Using measure of association for modifying DAGs}
\label{sec:modification}

The idea behind using the measure of association for modifying DAGs is that,
for any given model and a dataset, we can use the condtiional measure of
association to compute the amount of correlation in the data that is still not
explained by the model. Based on this, we can compute how much improvement in
the explanation would happen if we were to add an edge between variables. This
can then be ranked using the maximum improvement. Give some examples here.

@@

\section{Web Tool}
\label{sec:web}
Based on the approach outlined in the previous section, we built a web-based
tool that researchers can upload their dataset to and apply this method to
interactively draw models. Users can start by uploading their datasets. The web
interface should then automatically show them all the correlated variables in a
graphical representation. The red colored edges represent potential new edge
between the variables.

@@

\subsection{Using Large Language Models as Experts}
A lot of recent work has focused on finding pairwise causal direction among
variables using Large Language Models. In this analysis, instead of using the
oracle to decide the direction of edges, we used GPT4 to give us the direction
of the edges based on description of the variables. As GPT4 has already
memorized many of these models, we encoded the variable names using a random
string and provided the description of the variable to let it decide the
direction of the edge.

\section{Conclusions}
